\documentclass[letterpaper, 11pt]{article}

% Packages
\usepackage{fontspec}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{polyglossia}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\usepackage{tabularx}
\usepackage{xparse}
\usepackage{hyperref}
%% Debug
%\usepackage[l2tabu, orthodox]{nag}

% Settings
%\setmainfont{}            % Font (e.g., Times New Roman)
\setmainlanguage{english} % Language
\geometry{margin=1in}     % Margins
%% Header/Footer
\pagestyle{fancy}
\cfoot{\thepage{} of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{14pt}
%% Color Box
\tcbset{%
  colframe=white!93!black,
  colback=white!93!black,
  valign=center,
  size=fbox,
  sharp corners,
  height=18pt,
}
%% Metadata
\hypersetup{%
  pdftitle=Scott Clark -- Resume,
  pdfsubject=Resume,
  pdfauthor=Scott Clark,
  pdfcreator=Scott Clark,
  pdfproducer=Scott Clark,
  hidelinks,
}
%% Debug
%\geometry{showframe}

% Commands
\renewcommand{\section}[1]{%
  \begin{tcolorbox}
    \textsc{\textbf{\large{#1}}}
  \end{tcolorbox}
}
\newcommand{\entry}[4]{%
  \begin{tabularx}{\linewidth}{@{}Xr@{}}
    \textbf{#2} & \textbf{#1} \\
    #3          & #4          \\
  \end{tabularx}
}

% Macros
\DeclareDocumentCommand{\website}{mo}{%
  \IfNoValueTF{#2}%
  {\href{http://#1}{\texttt{#1}}}%
  {\href{http://#1}{\texttt{#2}}}%
}
\newcommand{\twitter}[1]{\website{twitter.com/#1}[@#1]}
\newcommand{\email}[1]{\href{mailto:#1}{\texttt{#1}}}

\begin{document}
  \begin{tabularx}{\linewidth}{@{}Xr@{}}
    \textbf{\Large{Scott Clark}} & \textbf{\today}                       \\
    \email{scott@scottclark.io}  & \website{scottclark.io}               \\
    \twitter{DrScottClark}       & Not looking for new job opportunities \\
  \end{tabularx}

  \section{Education}

  \entry{2008 -- 2012}{Ph.D. Applied Mathematics, M.S. Computer Science}{Cornell University}{Ithaca, NY}
  \begin{itemize}
    \item{Department of Energy Computational Science Graduate Fellow (Full Scholarship, 4 years)}
    \item{Machine Learning, Data Science, Data Mining in bioinformatics and global optimization}
  \end{itemize}

  \entry{2004 -- 2008}{B.Sc. Mathematics, B.Sc. Computational Physics, B.Sc. Physics}{Oregon State University}{Corvallis, OR}
  \begin{itemize}
    \item{Graduated Magna Cum Laude with minors in Actuarial Sciences and Mathematical Sciences}
  \end{itemize}

  \section{Research and Work Experience}

  \entry{Nov 2014 -- \ldots}{Co-founder and CEO}{SigOpt Inc.}{San Francisco, CA}
  \begin{itemize}
    \item{Helping lead a world class team to eliminate expensive trial and error from every experts workflow. Using cutting edge optimization behind a simple API to help tune machine learning models and build better products in a variety of fields.}
  \end{itemize}

  \entry{Jul 2012 -- Dec 2014}{Data Mining Engineer and Lead on Ad Targeting Team}{Yelp Inc.}{San Francisco, CA}
  \begin{itemize}
    \item{\textbf{Optimization:} Co-developed and led team for MOE: the Metric Optimization Engine (\website{github.com/Yelp/MOE}, an \textbf{open source} optimization framework), found significant gains in different metrics across the organization using Bayesian Global Optimization algorithms.}
    \item{\textbf{Targeting:} Implemented multi-armed bandit strategies for ad selection, sole targeting engineer on mobile app ads rollout, developed new location-based targeting algorithms, advised and helped develop other machine learning and math based targeting projects.}
    \item{\textbf{Recruiting:} Created, implemented, and directed \website{yelp.com/dataset\_challenge}, gave tech talks across the country, led events, gave hundreds of technical interviews, closed candidates.}
  \end{itemize}

  \entry{Summer 2011}{Financial Software Development Intern}{Bloomberg L.P.}{New York, NY}
  \begin{itemize}
    \item{Implemented statistical models to perform forward and backward portfolio analysis}
  \end{itemize}

  \entry{Summer 2010}{Researcher in Analysis Group under Dr. Zhong Wang}{DOE Joint Genome Institute (Lawrence Berkeley National Lab)}{Walnut Creek, CA}
  \begin{itemize}
    \item{Used machine learning to mine TBs of genome data efficiently using novel likelihood function}
  \end{itemize}

  \entry{Summer 2009}{Researcher in Metagenomics Group under Dr. Nick Hengartner}{Los Alamos National Laboratory}{Los Alamos, NM}
  \begin{itemize}
    \item{Used statistical models to discover sequence alignments using parallel algorithms on GPUs}
  \end{itemize}

  \entry{2005 -- 2008}{Research Assistant under Prof. Malgorzata Peszynska and Prof. Rubin Landau}{Oregon State University}{Corvallis, OR}
  \begin{itemize}
    \item{Finite element analysis with uncertainty and web-based teaching in \texttt{Java}}
  \end{itemize}

  \entry{Summer 2007}{NSF REU Research Assistant under Prof. Steven Tomsovic}{Max Plank Institute for the Physics of Complex Systems}{Dresden, Germany}
  \begin{itemize}
    \item{Research on extreme value statistics in \texttt{MATLAB} and \texttt{FORTRAN}}
  \end{itemize}

  \entry{Summer 2006}{NSF REU Research Assistant under Prof. Daniel Cox}{University of California, Davis}{Davis, CA}
  \begin{itemize}
    \item{Computational biophysics research as applied to protein folding in \texttt{Java}}
  \end{itemize}

  \section{Writing and Awards}

  \begin{itemize}
    \item \textbf{2016 Forbes 30 Under 30:} Enterprise Tech. \website{onforb.es/1OILpBZ}
    \item \textbf{Department of Energy Computational Science Graduate Fellow:} Four year full fellowship. $\sim$20 awarded nationally per year. Won the Communicating Science award (\website{bit.ly/VbcTZK}).
    \item \textbf{SigOpt Blog:} Posts talking about using SigOpt to optimize everything (\website{blog.sigopt.com}).
    \item \textbf{Yelp Blog:} Wrote several posts announcing the open sourcing of MOE, the Yelp Dataset Challenge and more. \website{bit.ly/1x73xdr}, \website{bit.ly/1oCCZvv}, \website{bit.ly/1sOsEBS}, \website{bit.ly/1plX7Hk}
    \item \textbf{Press:} WSJ: \website{on.wsj.com/VaOvqQ}, Cornell: \website{bit.ly/1oB2dzm},  DIEXIS: \website{bit.ly/1oofbl4}
  \end{itemize}

  \section{Skills}

  \begin{itemize}
    \item \textbf{Numerical Analysis and Computer Science:} Machine Learning, Data Mining, Optimization, Computational Science, Artificial Intelligence, Linear Algebra, Monte Carlo Methods, ODEs, PDEs, Iterative Methods, Parallel Programming, Distributed Systems, Data Structures
    \item \textbf{Tech Stack:} Python, numerical libraries, linux, git, vim
    \item \textbf{Public Speaking:} I've given several hundred technical talks to audiences at machine learning conferences, Fortune 500 boards, and beyond.
    \item Exploring and implementing ideas. Give me an API/dataset and a problem and I will figure it out.
  \end{itemize}

  \section{Selected Open Source Projects}
  
  \entry{2014 -- \ldots}{Examples of using SigOpt to tune ML algorithms}{SigOpt Examples (\website{github.com/sigopt/sigopt-examples})}{Python}
  \begin{itemize}
    \item{Examples of using SigOpt to tune everything from sklearn to beating Vegas and beyond.}
  \end{itemize}

  \entry{2010 -- 2015}{A global, black box optimization engine for real world metric optimization}{MOE: Metric Optimization Engine (\website{github.com/Yelp/MOE})}{Python, C++, CUDA}
  \begin{itemize}
    \item{Implemented throughout Yelp, optimizing ad metrics. 2nd most popular open source project.}
    \item{Talk: \website{bit.ly/1plYZA2}, Slides: \website{slidesha.re/1zOrOJy}, Blog: \website{bit.ly/1x73xdr}}
    \item{Presented to executives, universities, conferences and companies around the country.}
  \end{itemize}

  \entry{2010 -- 2013}{Probabilistic evaluation of genome assemblies}{ALE: Assembly Likelihood Estimator (\website{github.com/sc932/ALE})}{C, Python}
  \begin{itemize}
    \item{Uses statistical function to score and rank genome assemblies, published in Bioinformatics}
  \end{itemize}
\end{document}
